Trends of SDR in Thessaloniki

### 2023-07-12 Article.Rmd
Commit 2023-07-13 00:10

The maximum difference $X$ between the change in measured irradiance and the change in clear sky
irradiance over each measurement interval.

\begin{gather}
x_i = \text{SDR}_{i+1} - \text{SDR}_{i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM1} \\
x_{CS,i} = \text{SDR}_{CS,i+1} - \text{SDR}_{CS,i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM2} \\
X_i = \max{\left \{ \left | x_i - x_{CS,i} \right | \right \}} \label{eq:VSM3}
\end{gather}

@@

<!-- ### Data selection -->
Due to a significant measurement uncertainty near, the horizon, we have to exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
On the latter instances, Sun is systematically, not visible by the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1 \text{au}$, in order to compensate for the Sun's intensity variability, using a homogenized time series of satellite TSI observations.
The TSI data we use, comes from NOAA [@Coddington2005], it overlaps with our data, and is interpolated to match with the time step of the data.
<!-- The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @LASP2023 (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).-->
As a result, we can present all radiation data as a fraction of Sun's TSI.

After the preparation of the data, we have $`r SDR_N_All`$  1-minute measurements, of which,
$`r signif(100 * SDR_N_Clear / SDR_N_All, 3)`\%$ 
are characterized with clear-sky condition, and the rest 
$`r signif(100 * SDR_N_Cloud / SDR_N_All, 3)`\%$
with cloud-sky conditions.

>>>>

The maximum difference $X$ between the change in measured irradiance and the change in clear sky irradiance over each measurement interval, must be lower than a threshold (Eq.\ \ref{eq:VSMcr}).

\begin{gather}
x_i = \text{SDR}_{i+1} - \text{SDR}_{i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM1} \\
x_{\text{CSref},i} = \text{SDR}_{\text{CSref},i+1} - \text{SDR}_{\text{CSref},i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM2} \\
X_i = \max{\left \{ \left | x_i - x_{\text{CSref},i} \right | \right \}} \label{eq:VSM3}
\end{gather}

@@

<!-- ### Data selection -->
Due to a significant measurement uncertainty near the horizon, we have to exclude all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
On the latter instances, Sun is systematically, not visible by the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1\,\text{au}$, in order to compensate for the Sun's intensity variability, using a homogenized time series of satellite TSI observations.
The TSI data we use, comes from NOAA [@Coddington2005], it overlaps with our data, and is interpolated to match with the time step of the data.
<!-- The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @LASP2023 (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).-->
As a result, we can present all radiation data as a fraction of Sun's TSI. 
After the preparation of the data, we have $`r SDR_N_All`$  1-minute measurements, of which,
$`r signif(100 * SDR_N_Clear / SDR_N_All, 3)`\%$ 
are characterized with clear-sky condition, and the rest 
$`r signif(100 * SDR_N_Cloud / SDR_N_All, 3)`\%$
with cloud-sky conditions.

.......!!!.......
